The imprint of global magma oceans on exoplanet demographics

### 2022-08-22 src/tex/ms.tex
add example statpower plot, caption

>>>>

\begin{note}
   The fidelity of a future detection or falsification of a magma ocean signature will depend on the significance with which the null hypothesis can be excluded.
   As a consequence, instrumentation and survey strategy aiming at testing the hypothesis should aim at maximizing the probability of a true positive detection given the existence of the effect.
   This is called the statistical power of the test.
   Before turning to mission design trades that influence the statistical power in Sect.~\ref{sec:mission-design-trades}, we explore its behavior as a function of various free parameters of the magma ocean model.
    ...
\begin{figure*}[ht!]
%    \script{figurescript.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/example_statistical_power.pdf}
        \caption{
        Statistical power of a magma ocean hypothesis test as a function of model parameters.
        }
        \label{fig:statistical_power}
    \end{centering}
\end{figure*}

\end{note}
